Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-04-23 outputs/paper/paper.Rmd
Result session writing started

1) Positive: Drug Addicts, Welfare,

@@

3) Unchanged: Childcare, Crime rates, Education, Energy, Environment, Mass Transportation, Park and recreation, Roads, Scientific research, Social security.

natheal, natsci, natroad, natenrgy and natcrime appeared in the models insignificant

```{r, include = FALSE}
d_data <- rbind(reduced_data1, reduced_data2)
model1 <- lm(natfare ~ natdrug, data = d_data)
model2 <- lm(nataid ~ natarms + natcity + natheal + natrace, data = d_data )
model3 <- lm(natchld ~ natcrime + nateduc + natenrgy + natenvir + natmass + natpark + natroad + natsci + natsoc, data = d_data)
```

@@

@@

U.S. Census Bureau (2021). Population estimates. Retrieved from https://www.census.gov/quickfacts/fact/table/US/PST045221.

>>>>

1) Positive: Drug Addicts, Welfare

@@

3) Unchanged: Childcare, Crime rates, Education, Energy, Environment, Mass Transportation, Park and recreation, Roads, Scientific research, Social security

4) Government responsibility : helppoor, helpsick, eqwlth

natheal, natsci, natroad, natenrgy and natcrime appeared in the corresponding models insignificant. However, this does not mean that I needed to re-arrange the groups, rather it shows that there is no linear relations with chosen y- value. Also, since different changes in percentage is evident, they must belong to original groups, and further interpretation is going to be made in result and discussion session.

```{r, include = FALSE}
d_data <- rbind(reduced_data1, reduced_data2)
model1 <- lm(natfare ~ natdrug, data = d_data)
model2 <- lm(nataid ~ natarms + natcity  + natrace + natheal, data = d_data )
model3 <- lm(natchld ~ natcrime + nateduc + natenrgy + natenvir + natmass + natpark + natroad + natsci + natsoc, data = d_data)
model4 <- lm(helppoor ~  helpsick + eqwlth, data = d_data)
```

@@

In this session, I am going to summarize results from model and data session.

First, let's take a look at the positive group. This also includes government responsibility group excluding helppoor as they both present voices on more government actions needed. Following that, figure \@ref(fig:fig6), figure \@ref(fig:fig10), figure \@ref(fig:fig20), and figure \@ref(fig:fig21) belong to this group. One interesting result is national spending levels on drug figure \@ref(fig:fig6). According to CDC, death from overdoes in U.S is increasing over years, but the fact that respondents moved to "About right" on the national spending level contradicts with the CDC data, although majority of them answered "Too little", 70% in 2018 and 61% in 2021. Unlike small increase in drug overdoes death in other years, it noticeably increased during the pandemic. The movement conveys an important message here: indifference. During the pandemic, especially between 2020 and 2021, there was strict lock down policy in U.S. Other than essential workers, most had to stay at home, which caused for people to be indifferent about their surroundings. 
In addition to the indifference from the lock down, it also brought financial problems. People who could work remote was rare comparing to people who could not. In other words, there was serious layoffs although government gave financial aids. This naturally caused many to consider more actions and funds were needed, which appeared in welfare (figure \@ref(fig:fig10)), helppoor (figure \@ref(fig:fig20)) and eqwlth (figure \@ref(fig:fig21)).

Second, let's explore into the negative group: Figure \@ref(fig:fig1), Figure \@ref(fig:fig2), Figure \@ref(fig:fig4), Figure \@ref(fig:fig11), and Figure \@ref(fig:fig14).
They all show increase in "Too much". There were few things that were showed very interesting results. One was health part. It is true that majority answered "Too little" for national spending on healthcare in both years. However, it dropped by 5.8%. Although this is little above from the standard of change I set in the model session, and it did not solely fit into the group, considering 2020 survey was conducted during the pandemic, it was surprising. According to Forbes, critical care beds per capita in U.S is the highest In other words, unlike other countries, U.S was comparatively able to handle serious patients well. Also, as the pandemic went on, the virus got weaker, which enabled people to treat themselves at home. I suspect that this is why there was drop in "Too little". Therefore, health must stay in the negative group. In addition to the health part, race presented very interesting result as well. Black Lives Matter was a big issue during 2020,however, voice for more actions dropped over the years. It is absolutely true that there should not be any discrimination against races. However, violence cannot be justified under the name of equality. After George Floyd was murdered by a police officer in May 25, 2020, serious riots and looting occurred all over U.S. I think the drop in "Too little" was appeared as a counteraction of the violence. The rest variables make sense if you think of the pandemic situation. During the pandemic, not only vaccines were more needed than guns, but taking care of own nation came first than helping other countries. Therefore, it is natural to observe the negative in arms, foreign aids and big city problems.

Last is the unchanged group:  Figure \@ref(fig:fig3), Figure \@ref(fig:fig5), Figure \@ref(fig:fig7), Figure \@ref(fig:fig8), Figure \@ref(fig:fig9), Figure \@ref(fig:fig12), Figure \@ref(fig:fig13), Figure \@ref(fig:fig15), Figure \@ref(fig:fig16) and Figure \@ref(fig:fig17).
This group can be interpreted as a group that is absolutely essential in society. For instance, no matter what we face, education 
1. Essential
2. Indifference regarding the virus.

@@

U.S. Census Bureau (2021). Population estimates. Retrieved from https://www.census.gov/quickfacts/fact/table/US/PST045221.
https://www.forbes.com/sites/niallmccarthy/2020/03/12/the-countries-with-the-most-critical-care-beds-per-capita-infographic/?sh=347315dc7f86
